\documentclass[]{article}
\setlength\parindent{0pt}

% Custom itemize bullet
\def\labelitemi{--}

% Define a new section on resume
\def \mysection[#1]{
\vspace{.4cm}
\hrule
\vspace{.4cm}
{\large #1 \par}
\vspace{.3cm}
}

\usepackage{color,graphicx,hyperref,multirow,enumitem}
\usepackage[margin=1.5in]{geometry}

\definecolor{linkcolour}{rgb}{0,0,0}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\pagenumbering{gobble}

\begin{document}

\par{\centering {\Huge Joshua Howard }\par} 

\vspace{.3cm}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}l c r@{}}
Email: \href{mailto:joshthoward@gmail.com}{joshthoward@gmail.com} &
Phone: 423-834-2872 &
Website: \href{http://joshthoward.info}{joshthoward.info}
\end{tabular}}

\mysection[Summary] 
An accomplished machine learning and big data engineer with experience in consulting and product development and prototyping. 

\mysection[Experience]
\textbf{Research Scientist} at Pindrop, Inc. \hfill June 2017 - Present
\begin{itemize}[leftmargin=*, topsep=.5em, itemsep=.25em]
\item Created and enhanced core capabilities of fraud detection and biometric authentication products using machine learning in the FinTech and IoT spaces
\item Technical lead for product deployment at Morgan Stanley, Fifth Third Bank, MUFG Union Bank, PSCU, Northwestern Mutual, and Jackson National Life
\item Team lead for authentication and big data competencies 
\end{itemize}

\textbf{Machine Learning Engineer} at IERUS Technologies, Inc. \hfill May 2016 - June 2017
\begin{itemize}[leftmargin=*, topsep=.5em, itemsep=.25em]
\item Developed high performance machine learning services while consulting for Leidos, Raytheon, NSWCCD, and MDA
\item Led ISAR and EOIR image classification projects as machine learning SME
\item Authored and reviewed multiple SBIR and STTR grants
\end{itemize}

\textbf{Graduate Assistant} at The Georgia Institute of Technology \hfill Jan. 2015 - Apr. 2016
\begin{itemize}[leftmargin=*, topsep=.5em, itemsep=.25em]
\item Developed a PoC application for machine learning based disease diagnosis featured by school of electrical engineering
\item Led recitations in multivariate calculus, linear algebra, and discrete mathematics
\end{itemize}

\textbf{Undergraduate Researcher} at Kennesaw State University \hfill Jan. 2014 - Dec. 2014
\begin{itemize}[leftmargin=*, topsep=.5em, itemsep=.25em]
\item Applied control systems engineering concepts to macro environmental models, and implemented algorithms for determining optimal controls for these models
\item Contributions were recognized at the university's 2014 Symposium of Student Scholars
\end{itemize}

\mysection[Education]
\textbf{MS, Computational Science and Engineering}\hfill May 2016\\Georgia Institute of Technology\hspace{10pt}\\

\textbf{BS, \textit{summa cum laude}, Mathematics}\hfill Dec. 2014\\Kennesaw State University\hspace{10pt}

\vspace{.3cm}
\hrule

\pagebreak
\mysection[Certifications and awards]
\begin{itemize}[leftmargin=*, topsep=.5em, itemsep=.25em]
\item AWS Certified Big Data - Specialty
\item AWS Certified Developer - Associate
\item National Science Foundation STEM Fellowship
\end{itemize}

\mysection[Skills]
Python, Rust, JVM (Scala, Java, and Groovy), web development (Javascript, HTML, and CSS), data processing (SQL, NoSQL, Hadoop, Spark, Presto, Hive, HBase, and Hue), TensorFlow, Theano, Scikit Learn, Docker, Jenkins, Git, Linux, OSX, Amazon Web Services \\
\hrule
\end{document}
